\documentclass[10pt,letterpaper,withhyper]{altacv}

% Page layout / font setup
\geometry{left=1cm,right=1cm,top=1cm,bottom=0cm,columnsep=0.6cm}
\usepackage{fontspec}
\setmainfont{TeX Gyre Heros} %free font change - resolves common errors

% Make section headers smaller
\renewcommand{\cvsectionfont}{\Large\bfseries}

% Make subsection headers smaller (used in \cvevent titles)
\renewcommand{\cvsubsectionfont}{\normalsize\bfseries}

% Colors
\definecolor{accent}{HTML}{111111}
\definecolor{heading}{HTML}{000000}
\definecolor{body}{HTML}{333333}
\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{accent}
\colorlet{body}{body}

% Layout engine
\usepackage{paracol}
\columnratio{0.7}

\begin{document}
\sloppy

%%
%%
% Header - some tagline redundancy
\name{Bennett M. Anderson}
\tagline{Ames, IA • bmarc@iastate.edu • 815-821-9604 • Bennett-Anderson.com}
\personalinfo{
  \email{bmarc@iastate.edu}
  \phone{815-821-9604}
  \location{Ames, IA}
  \linkedin{linkedin.com/in/bennett-m-anderson}
  \github{github.com/B-M-Anderson}
}
\makecvheader

\begin{paracol}{2}

%
% Right Column First
\switchcolumn

%%
%%
% Education Section
\cvsection{Education}
\cvevent{B.S. in Biomedical Engineering}{Iowa State University  -  3.53/4.00}{Expected May 2027}{}
\begin{itemize}
\item Minor in Pharmacology
\end{itemize}

\divider

%%
%%
% Skills Section
\cvsection{Skills \& Software}

\cvtag{MATLAB}
\cvtag{Python}
\cvtag{LaTeX}
\cvtag{SnapGene}
\cvtag{PyMOL}
\cvtag{SolidWorks}
\cvtag{Experimental Design}
\cvtag{Genomic Data Alignment}
\cvtag{Protein Visualization}
\cvtag{Microbiology Techniques}
\cvtag{Technical Presentation}
\cvtag{Git/GitHub}



\divider

%%
%%
% Involvement Section
\cvsection{Local Involvement}
\cvevent{Tutor}{Iowa State University}{Feb 2025 -- May 2025}{}
\begin{itemize}
\item Supported students in physics and biology.
\end{itemize}

\divider

\cvevent{Model}{ISU Fashion Show}{Jan 2024 -- Apr 2024}{}
\begin{itemize}
\item Walked runway for 2 outfits + designer set.
\item Collaborated with designers + directors.
\end{itemize}

\divider

\cvevent{Volunteer}{Food at First}{2023 -- 2024}{}
\begin{itemize}
\item Helped provide food for community members in need.
\end{itemize}

%%
%%
% RIGHT COLUMN (now switch once)
\switchcolumn


%
% Notificaiton header
\begin{center}
\colorbox{accent!10}{%
  \parbox{\dimexpr\linewidth-2\fboxsep}{%
    \centering
    All Personal Projects \& Publications Available for Viewing\\
    @ Bennett-Anderson.com
  }
}
\end{center}

%%
%%
% Experience Section
\cvsection{Practical Experience}
\cvevent{Undergraduate Research Assistant}{ISU Department of Chemical and Biological Engineering}{Jan 2025 -- Present}{}
\begin{itemize}
\item Designs experiments for identifying genetic knockdowns and validating selections.
\item Performs transformations, minipreps, PCR, gels, and other standard protocols.
\item Uses MATLAB/Python for low-bp alignment of noisy genomic sequences.
\item Uses PyMOL for ligand binding + structural comparison.
\item Collaborates with graduate student, meets with PI, and presents semesterly.
\item BSL-1 trained with strong microbiology/biochemistry fundamentals.
\end{itemize}

\divider

%%
%%
% Highlighted Projects Section
\cvsection{Highlight / Recent Personal Project}

\cvevent{Bennett-Anderson.com}{Personal Website}{}{}
\begin{itemize}
\item Designed and deployed a responsive portfolio site using Next.js, TypeScript, and Tailwind CSS.
\item Implemented multi-device compatability of features, dark mode toggles, animated navigation, and project showcase with GitHub integration in a system designed for easy expansion.
\item Hosted on Vercel with custom domain; demonstrates full-stack web development, UI design, and adaptive ability to quickly become productive with unfamilliar tools.
\end{itemize}
\divider


%%
%%
% Leadership Section
\cvsection{ISU Leadership Activities}
\cvevent{Peer Mentor, BME 1040}{}{Jul 2024 -- Dec 2024}{}
\begin{itemize}
\item Led a roughly 20 freshmen class; weekly custom lesson plans.
\item Held 1:1 goal-planning and support sessions.
\item Coordinated and conducted events fostering positive faculty and student relationships.
\end{itemize}

\divider

\cvevent{Lap Simulation \& Testing Engineer}{ISU FSAE Team}{Aug 2023 -- Nov 2024}{}
\begin{itemize}
\item Programmed MATLAB acceleration simulation to influence top-level design choices. 
\item Modeled parts in SolidWorks for concept demos.
\item Mentored new members; contributed to test days.
\end{itemize}


\end{paracol}

%
%% footnote
\begin{center}
\vspace*{-11pt}
    \underline{\small\textit{Document personally designed in \LaTeX{}}}
\end{center}

\end{document}
